### 2019-04-08 5_evaluation.tex
Trimming some text to make things fit again.
Get the figures reorganized again.
add one more explaination why some systems are missing in figures

The vast majority of systems achieve or nearly achieve peak FLOPS. Some
systems reserve a number of cores (usually 1 or 2) for internal
runtime usage; these systems take a minor hit in peak FLOPS compared
to systems which share all cores between the application and runtime. Some of the
slower systems struggle to achieve peak FLOPS, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes it prohibitively
expensive to run larger problem sizes. For example, the Spark job in
this configuration ran for over 6 hours.

Figure~\ref{fig:efficiency} shows efficiency (as a percentage of
peak FLOPS) plotted against task granularity. This plot is
used to calculate METG(50\%), as described in Section~\ref{sec:metg}. The
red, dashed line shows the point where 50\% efficiency is achieved.

In most cases, task granularity asymptotes prior to the 50\% efficiency point,
though some systems continue to improve as efficiency continues
to drop. Accounting for this effect is one of the main arguments in
favor of METG with a reasonable efficiency threshold instead of
measuring task scheduling throughput of empty tasks
(effectively METG(0\%)). Measuring performance using empty tasks can
reward implementation strategies, such as devoting nearly 100\% of
system resources to the runtime system, that make no sense for real
applications.

@@

\input{e7_bytes}

@@

@@

@@

\input{e4_radix}

@@

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs. Some of the slower systems
are omitted from comparisons with more complicated dependence
patterns, as they did not complete in reasonable time.

>>>>

The vast majority of systems achieve or nearly achieve peak FLOPS. Some
systems reserve a number of cores (usually 1 or 2) for internal
runtime usage; these systems take a minor hit in peak FLOPS compared
to systems which share all cores between the application and runtime. Some of the
slower systems struggle to achieve peak FLOPS, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes this prohibitively
expensive. For example, the Spark job in
this configuration ran for over 6 hours.

Figure~\ref{fig:efficiency} shows efficiency (as a percentage of
peak FLOPS) plotted against task granularity. This plot is
used to calculate METG(50\%), as described in Section~\ref{sec:metg}. The
red, dashed line shows the point where 50\% efficiency is achieved.
In most cases, task granularity asymptotes prior to the 50\% efficiency point,
though some systems continue to improve as efficiency continues
to drop. Accounting for this effect is one of the main arguments in
favor of METG with a reasonable efficiency threshold instead of
measuring task scheduling throughput of empty tasks
(effectively METG(0\%)). Measuring performance using empty tasks can
reward implementation strategies, such as devoting nearly 100\% of
system resources to the runtime system, that make no sense for real
applications.

@@

@@

% FIXME: why is Charm++ slow?

@@

% FIXME: why compute-bound kernels?

@@

\input{e7_bytes}
\input{e4_radix}

@@

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs. Some of the slower systems
are omitted from comparisons with more complicated dependence
patterns, as they did not complete in reasonable time 
or reach METG(50\%) even with the largest problem size.
